---
title: "p8105_hw5_zz3168"
author: "Zixuan Zhang"
date: "2023-11-11"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(patchwork)

knitr::opts_chunk$set(
echo = TRUE,
warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%")

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis")

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1
```{r}

```

# Problem 2
### Tidy the import data
```{r}
full_data =
  tibble(
    file_df = list.files("data/zip_data"),
    path = str_c("data/zip_data/", file_df)
  ) |> 
  mutate(
    data = map(path,read_csv)
  ) |> 
  unnest(data) |>
   mutate(
    file_df = str_replace(file_df, ".csv", ""),
    group = str_sub(file_df, 1, 3)) |>
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observations"
  ) |> 
  select(group, subject = file_df, week, observations)
  

  
```

##### Making the Plot
```{r}
full_data |> 
  ggplot(aes(x = week, y = observations, group = subject, color = subject)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group) +
   labs(
    title = "Observations on each subject over time",
    x = "Week",
    y = "Observations"
  )
  
  
```
The ggplot shows that from the 1 week to the 8 week, we can observe from the icon that the data of the experimental group has been increasing and is higher than that of the control group. The data of the control group does not seem to change according to the passage of time, so we It can be concluded that the values of the experimental group are generally higher than those of the control group.

# Problem 3
